Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-16 main.Rmd
(a) and (b) for both circular and quasi-circular figures

(ref:circular-dow) a. Index sets for some linear and circular granularities. b. Circular granularities can be constructed by slicing the linear granularity into pieces and stacking them.

>>>>

(ref:circular-dow) Index sets for some linear and circular granularities (a). Circular granularities can be constructed by slicing the linear granularity into pieces and stacking them (b).
